% ------------------------------------------------------------------------
% ------------------------------------------------------------------------
% ------------------------------------------------------------------------
%                                Abstract
% ------------------------------------------------------------------------
% ------------------------------------------------------------------------
% ------------------------------------------------------------------------
\chapter*{ABSTRACT}

\footnotesize{
\begin{description}
    \item[TITLE:] DESIGN OF AN EXTENSIBLE SOFTWARE PLATFORM FOR THE DEPLOYMENT, EXECUTION AND VISUALIZATION OF ALGORITHMS DEDICATED TO COMPUTER 
    \astfootnote{Degree work}
    
    \item[AUTHOR:] JUAN SEBASTIAN MARCON CABALLERO 
    \asttfootnote{Faculty of Physical-Mechanical Engineering. School of Systems and Computer Engineering. Advisor: Fabio Martínez Carrillo, Ph.D}
    
    \item[KEYWORDS:] DEDICATED ALGORITHMS, COMPUTER VISION, MACHINE LEARNING, DEPLOYMENT, EXECUTION, DISPLAY, COMPATIBILITY, EXTENSIBLE, SOFTWARE STRUCTURE.
    
    \item[DESCRIPTION:] The boom today, in areas such as computer vision and artificial intelligence, have allowed us to support and solve a large number of problems in various areas of knowledge. Many of these methods have evolved into robust applications that operate successfully in the market and solve problems related to data analysis and simplification of repetitive tasks. However, some research proposals oriented to the design of these algorithms do not evolve as technological applications due to the existing difficulty in the process of deployment and execution of the different models that compose them, thus requiring the design of software that offers an adequate infrastructure for deployment, managing complexity, managing heterogeneity, and extensibility of the solution. \\
    The characteristic tools of computer science are focused on solving optimization problems and modeling machine learning algorithms. However, these algorithms lack a clear and uniform software structure, which leads to functional prototypes, but with little usability, even by other experts in the same area. Among others, these functional algorithms have multiple software dependencies that generate incompatibility problems and difficulty operating in different environments and operating systems. Based on the foregoing, this project aims to design a software platform that allows the use, visualization and deployment of different technologies based on machine learning and computer vision.


\end{description}
}\normalsize
% ------------------------------------------------------------------------ 
